Learning and comparing functional connectomes between populations

### 2012-12-26 paper.tex
Iterate on paper

First, we focus on detecting where the connectivity matrices estimated in
the previous section differ.
\paragraph{Mass-univariate approaches}
%
The most natural approach is to do a linear model on each coefficient of
the connectivity matrices, as in \cite{lewis2009,grillon2012}.
This approach is similar to the second-level
analysis used in mass-univariate brain mapping, and will give rise to
many of the well-known techniques used in such a context, such as the
definition of second-level design, with possibly the inclusion of
confounding effects, and statistical tests (T tests or F tests) on
contrast vector. Importantly, in order to work with Gaussian-distributed
correlations, it is necessary to apply a Fisher Z
transform\footnote{See 
\url{http://en.wikipedia.org/wiki/Fisher_transformation}
or \cite{anderson1958}, section 4.2.3 for mathematical arguments}.
Note that in these settings, the Ledoit-Wolf estimator \cite{ledoit2004}
is probably a good choice to estimate the correlation matrix, as it is
parameter-less and gives good estimation performance without imposing any
restrictions on the data.
%
Correcting for multiple comparison can often severely limit statistical
power, as the number of tests performed scales as the square of the
number of regions used. Controlling for the false discovery rate (FDR)
mitigates this problem. Alternatively, as the assumption underlying the
Benjamini-Holchberg procedure for the FDR can easily be broken,
non-parametric permutations-based approaches give reliable approaches. In
particular, the max-T procedure
% NEEDREF: FDR for neuroimaging data, check the spelling of BH
is interesting to avoid the drastic Bonferroni correction when
controlling for multiple comparison in family-wise error rate.

% XXX: cite Ge "resampling-based multiple testing for microarray data
% analysis", and Nichols multiple comparison paper.

>>>>

First, we focus on detecting where the connectivity matrices estimated in
the previous section differ. \paragraph{Mass-univariate approaches}
%
The most natural approach is to do a linear model on each coefficient of
the connectivity matrices, as in \cite{lewis2009,grillon2012}. This
approach is similar to the second-level analysis used in mass-univariate
brain mapping, and will give rise to many of the well-known techniques
used in such a context, such as the definition of second-level design,
with possibly the inclusion of confounding effects, and statistical tests
(T tests or F tests) on contrast vector. Importantly, in order to work
with Gaussian-distributed correlations, it is necessary to apply a Fisher
Z transform\footnote{See
\url{http://en.wikipedia.org/wiki/Fisher_transformation} or
\cite{anderson1958}, section 4.2.3 for mathematical arguments}. Note that
in these settings, the Ledoit-Wolf estimator \cite{ledoit2004} is
probably a good choice to estimate the correlation matrix, as it is
parameter-less and gives good estimation performance without imposing any
restrictions on the data.
%
Correcting for multiple comparison can often severely limit statistical
power, as the number of tests performed scales as the square of the
number of regions used. Controlling for the false discovery rate (FDR)
mitigates this problem. Alternatively, as the assumption underlying the
Benjamini-Hochberg procedure \cite{benjamini1995} for the FDR can easily
be broken, non-parametric permutations-based approaches give reliable
approaches. In particular, the max-T procedure \cite{ge2003,nichols2001}
is interesting to avoid the drastic Bonferroni correction when
controlling for multiple comparison in family-wise error rate.
